---
title: "Geospatial Data Analysis of Food Restaurants in New Delhi"
author: "Koki Ando"
date: "4/13/2018"
output:
  html_document:
    code_folding: show
    highlight: tango
    number_section: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
## What is zomato?
[zomato](https://www.zomato.com/brisbane)

> Zomato is an Indian restaurant search and discovery service founded in 2008 by Deepinder Goyal and Pankaj Chaddah. It currently operates in 23 countries, including Australia and United States. It provides information and reviews on restaurants, including images of menus where the restaurant does not have its own website.
**From zomato's wikipedia**

## Motivation
1. Geospatial data analysis
2. Find the food restaurat food trend at any places

# Preparation
```{r}
library(tidyverse)
library(maps)
library(ggmap)
library(data.table)
zomato <- fread("https://s3-ap-southeast-2.amazonaws.com/koki25ando/zomato.csv", data.table = FALSE)
names(zomato)[3] <- "Country.Code"
names(zomato)[18] <- "Aggregate.rating"
names(zomato)[20] <- "Rating.text"
```

# Analysis
## Geospatial Analysis
### World Map Visualization
```{r}
world.map <- map_data ("world")
ggplot() + 
  geom_map(data=world.map, map=world.map,
           aes(x=long, y=lat, group=group, map_id=region),
           fill="white", colour="black") + 
  geom_point(data = zomato, aes(x = Longitude, y = Latitude), 
             colour = "red", alpha = .3) + 
  labs(title = "World Map of Food Restaurants from zomato dataset")
```

Seems like there are many data obeject from India. Thus, in this report, I am going to focus on food restaurant in India.

### India's data analysis

```{r}
india.zomato <- zomato %>% filter(Country.Code == 1)
india.map <- geocode("india")
india.coor <- c(lon = india.map$lon, lat = india.map$lat)
india.ggmap <- get_map(india.coor, zoom = 5, scale = 1)
ggmap(india.ggmap, base_layer = ggplot(india.zomato, aes(Longitude, Latitude))) + 
  geom_point(colour = "red", alpha = .3, size = .3) + 
  labs(title = "India's zomato data visualization")
```

### Which city to focus on?

```{r}
india.zomato$City %>% table()
```

New Delhi has the most of the restaurants in India.

#### Google Map visualization
```{r}
nd.zomato <- india.zomato %>% filter(City == "New Delhi")
new.delhi <- geocode("new delhi")
nd.coor <- c(lon = new.delhi$lon, lat = new.delhi$lat)
nd.map <- get_map(nd.coor, zoom = 12, scale = 1)
ggmap(nd.map) + 
  geom_point(data = nd.zomato,
         aes(x = Longitude, y = Latitude, colour = Aggregate.rating), alpha = .6, size = 1) +
  scale_colour_gradient(low = "yellow", high = "red", name = "Rating Score") + 
  labs(title = "Restaurants in New Delhi")
```

At this time, I tiried using ggmap package for the first time. Ggmap package enable us to access the google map images.<br/>
Restaurants are scattered throughout the city.

### Data Cleaning
```{r}
ggplot(nd.zomato) + geom_histogram(aes(Aggregate.rating)) +
  labs(x = "Rating Score")

nd.zomato <- nd.zomato %>% filter(Aggregate.rating != 0) 
```

Removed useless objects that are, in this case, restaurants with 0 raging point.
```{r}
mean.nd.restaurants <- mean(nd.zomato$Aggregate.rating)
ggplot(nd.zomato) + geom_histogram(aes(Aggregate.rating)) + 
  geom_vline(xintercept = mean(nd.zomato$Aggregate.rating), linetype="dotted", 
                color = "blue", size=1.5) +
  geom_text(aes(x=mean.nd.restaurants, 
                label=paste("Mean",":", round(mean.nd.restaurants,3)), y = 200), 
            colour="red",vjust = 3, text=element_text(size=11), family = "Times New Roman") + 
  labs(title = "Rating score of food restaurants in New Delhi", x = "Rating Score")
```

Plotting the mean of rating of restaurants.

### Pick up the restaurants whose rating scores are above the mean. Where are they located?

```{r}
top.nd.zomato <- nd.zomato %>% filter(Aggregate.rating > mean.nd.restaurants)
ggmap(nd.map) + 
  geom_point(data = top.nd.zomato,
         aes(x = Longitude, y = Latitude, colour = Aggregate.rating), alpha = .6, size = 1) + 
  scale_colour_gradient(low = "yellow", high = "red", name = "Rating Score") + 
  labs(title = "Popular Restaurants in New Delhi")
```

## Trend Food

### String Manipulation using Stringr

```{r}
food.type <- top.nd.zomato$Cuisines
japanese.restaurant <- str_detect(food.type, pattern = "Japanese")
top.nd.zomato[japanese.restaurant,] %>% nrow()
```

Unfortunately only 38 restaurants offer japanese food. The answer is No. Japanese food are not popular in New Delhi.

### What are the most polular food in New Delhi?
```{r}
food.category <- food.type %>% str_split(",", simplify = TRUE)
food.category <- data.frame(table(food.category))
food.category <- food.category[-1,]

food.category %>% arrange(desc(Freq)) %>% top_n(15) %>% 
  ggplot(aes(x = reorder(x = food.category, X = desc(Freq)), y = Freq)) + 
  geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  labs(title = "Popular Food in New Delhi", x = "Food Category")
```

There are some duplications for some reason. However, it is apparent that North Indian, Chinese and Italian food restaurants are popular in the city.<br/>
Thus, in this article, I'm going to focus on them.

```{r}
pop.food <- top.nd.zomato$Cuisines %>% str_split(pattern = ",") %>% str_detect(c("North Indian", "Chinese", "Italian"))
pop.top.nd.zomato <- top.nd.zomato[pop.food,]
ggmap(nd.map) + 
  geom_point(data = pop.top.nd.zomato,
         aes(x = Longitude, y = Latitude, colour = Rating.text)) + 
  labs(title = "Popular food restaurants in New Delhi") +
  scale_colour_discrete(name = "Rating")
```

## Which Suburb has the highest rating?

```{r}
top10.pop.top.nd.zomato <- 
  pop.top.nd.zomato %>% 
  group_by(Locality) %>% 
  summarise(Average.rating = mean(Aggregate.rating)) %>% 
  arrange(desc(Average.rating)) %>% head(n = 10)

top10.pop.top.nd.zomato %>% 
  ggplot(aes(x = as.factor(Locality), y = Average.rating)) + 
  geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 70, vjust = .5)) + 
  labs(title = "Top 10 rating Suburbs", x = "Suburb Name")
```

Extracted top 10 Suburb
```{r}
suburb <- top10.pop.top.nd.zomato$Locality
```


```{r}
ggmap(nd.map) + 
  geom_point(data = pop.top.nd.zomato %>% 
               filter(Locality %in% suburb) %>% 
               group_by(Locality) %>% 
               mutate(average.Rate = mean(Aggregate.rating)),
         aes(x = Longitude, y = Latitude, size = average.Rate, colour = Locality)) + 
  labs(title = "Map visualization of Top 10 Suburb's Rating score") + 
  scale_colour_discrete(name = "Suburb Name")
```
